Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-08-16 main.tex
reflection theorem

The situation is less clear cut when we study the curl or divergence operators in vector calculus.
We use the vector field spaces
\begin{align*}
    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
    ,
    \\
    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
    .
\end{align*}
Their members are vector fields whose distributional curls and divergences are in Lebesgue spaces. 
This only requires that certain sums of distributional partial derivatives are integrable, 
and hence these spaces are not classical Sobolev spaces of vector fields. 
Our objective is to find bounded potentials for the operators 
\begin{align*}
    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
    \qquad 
    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
\end{align*}
The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
We are interested in constants for inequalities such as 
\begin{align*}
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
    \| \bfv \|_{L^{p}(\Omega)}
    \leq 
    C_{\curl,\Omega,p}
    \| \bff \|_{L^{p}(\Omega)}
    ,
    \qquad 
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
    \| \bfv \|_{L^{p}(\Omega)}
    \leq 
    C_{\divergence,\Omega,p}
    \| f \|_{L^{p}(\Omega)}
    ,
\end{align*}
and whether these constants can be estimated by the operator norms of linear potential operators 
\begin{align*}
    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
    ,
    \quad 
    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
    .
\end{align*}

@@

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
    \begin{align*}
        M := |\patch_{\calT}(S)| \setminus T.
    \end{align*}
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \varphi : T \rightarrow M
    \end{align*}
    satisfying
    \begin{align*}
        \Lip( \varphi,      T ) \leq \Cvier{n}{k} \diam(T),
        \quad 
        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k} \diam(T),
    \end{align*}
    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$
\end{theorem}
\begin{proof}
    Without loss of generality, the barycenter of $S$ is the origin. 
    We derive the estimate in several steps. 
    \begin{itemize}
        \item 
        Let $I := M \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        So $J$ is in the boundary of $|\calT|$ and is disjoint from $S$.
        The subsimplex $S' \subseteq T$ that is complementary to $S$.
        such that $J$ is the union of exactly those faces of $T$ that contain $S'$.

        \item 
        We construct a new triangulation that contains $T$ and that is a star around $S$.
        For that purpose, we let $z'_{S}$ be the midpoint of $S'$. 
        We define a triangulation $\calS$ by the barycentric refinement of $T$. 
        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.

        We define another simplicial complex $\calS^c$ as follows:
        whenever $K \in \calS$ is an $n$-simplex, we replace the vertex $z_{S}'$ by new vertex opposite point $-z_{S}'$,
        giving us a simplex $K'$.

        In what follows, we also use $\calS''$, the simplicial complex obtained from $\calS'$ by barycentric subdivision of $S$.
        Then $\calS''$ is the local star around the barycenter $z_S$.

        \item 
        \todo{Reflect onto complement and estimate bi-Lipschitz constant}
        We introduce a new mapping $\Theta : |\calS| \rightarrow |\calS^c|$.

@@

@@

        We let $A_T \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.

@@

            \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x

@@

            \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x

@@

            \left( \vecone \cdot A^{-1} x \right)

@@

            \frac{x}{\|x\|} \left( \vecone \cdot A^{-1} x \right)

@@

            2 \left| \vecone \cdot A^{-1} x \right|

@@

            2 \sqrt{n} \cdot \sigma_{\max}(A^{-1}) 

@@

@@

                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A^{-1} y \|_{1} }{ \|y\|_2 } y

@@

                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } y

@@

                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A^{-1} y \|_{1} }{ \|y\|_2 } y

@@

            \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } 

@@

            \left| \|A^{-1} x\|_2 - \|A^{-1} y\|_2 \right|

@@

            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A^{-1}) 

@@

        where $\| A^{-1} y \|_{1} \leq \| A^{-1} x \|_{1}$ without loss of generality, we find 

@@

                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} } y

@@

                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } y

@@

                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} } y

@@

            \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } 

@@

            \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} }

@@

            2 \sigma_{\min}(A^{-1})^{-1} 

@@

        We recall that $\sigma_{\max}(A^{-1}) = \sigma_{\min}(A)^{-1}$ and $\sigma_{\min}(A^{-1})^{-1} = \sigma_{\max}(A)$.

        \item 
        Suppose that $S = \{v_0\}$ is a single vertex. 
        We construct a transformation from the vertex star around $S$ onto the Euclidean unit ball. 
        Without loss of generality, $S$ is at the origin. 
        For any $T \in \patch_{\calT}(S)$, we let $F_T$ be the transformation. 
        We define $F$ over $|\patch_{\calT}(S)|$ piecewise. 
        \todo{Complete}

        \item 
        \todo{Combine all this to get the final transformation.}

%         \item 
%         Let $\calU$ be the simplicial complex of dimension $n-1$ that contains precisely those facets of $T$ that do not contain $S$.
%         We write $Y := F( |\calU| )$. 
%         \todo{Shape of the outer patch $Y$, star-shaped geometry}
%         
%         \item 
%         We let $\sphere{n}_{\star} := \sphere{n} \setminus \{e_{n+1}\} \subseteq \bbR^{n+1}$ be the unit sphere without the North pole. 
%         Suppose that $\bar x \in \sphere{n}$ is a point on the unit sphere and $\bar x \neq e_{n+1}$. 
%         We define its stereographic projection as 
%         \begin{align}
%             \pi( \bar x ) 
%             = 
%             \sum_{i=1}^{n} \frac{x_i}{1 - x_{n+1}} e_{i}
%             .
%         \end{align}
%         This is a mapping $\pi : \sphere{n}_{\star} \rightarrow \bbR^{n}$. 
%         Its inverse is defined as follows: given $y \in \bbR^{n}$, we have 
%         \begin{align}
%             \pi^{-1}( y )
%             = 
%             \sum_{i=1}^{n} \frac{2 y_i}{1 + \| y \|^2} e_{i}
%             +
%             \frac{1 - \| y \|^2}{1 + \| y \|^2} e_{n+1}
%             .
%         \end{align}
%         \item 
%         Mirroring the unit sphere along the equator is expressed in stereographic coordinates by the involution 
%         \begin{align}
%             \mu : \bbR^{n} \rightarrow \bbR^{n},
%             \qquad 
%             y \mapsto \frac{y}{\| y \|}.
%         \end{align}
%         \item 
%         \begin{align}
%             G(y) := \| y \| \cdot \phi\left( \frac{y}{\|y\|} \right)^{-1} \frac{y}{\|y\|}
%         \end{align}
%         \item 
%         We combine these mappings:
%         \begin{align}
%             Q : \sphere{n} \rightarrow \sphere{n}, \qquad x \mapsto \pi^{-1} G^{-1} \mu G \pi(x)
%         \end{align}
%         We want to analyze its Lipschitz properties. \todo{Stuff}
%         \item
%         We have constructed a bi-Lipschitz mapping from the Euclidean unit sphere into itself.
%         We use the following result~\cite[Theorem~3]{alestalo2018radial}:
%         if $f : \sphere{n} \rightarrow \sphere{n}$ is any $L$-Lipschitz mapping from the Euclidean unit sphere into itself, 
%         then the radial extension $f : \ball{n} \rightarrow \ball{n}$ is an $L$-Lipschitz mapping from the Euclidean unit ball into itself.
%         Consequently, \todo{write out}
%         \item 
%         In total, we thus have 
%         \begin{align}
%             Q' := F^{-1} \pi^{-1} G^{-1} \mu G \pi F
%             .
        \end{align}
    \end{itemize}
\end{proof}

% Please cite the original version:
% Alestalo, P., & Trotsenko, D. A. (2018). Radial extensions of bilipschitz maps between unit spheres. Siberian
% Electronic Mathematical Reports, 15, 839-843. https://doi.org/10.17377/semi.2018.15.071
% Theorem 3: radial extension of bi lipschitz between unit spheres, with same constant

We recall a specialization of this result.

\begin{lemma}\label{theorem:starreflection:facepatch}

\end{lemma}

% https://mathoverflow.net/questions/232302/lipschitz-constant-of-cental-projection-of-unit-ball-to-surface-of-convex-body
% https://eudml.org/doc/258483
% https://math.stackexchange.com/questions/1476085/uniformly-convex-approximation-of-convex-domain
% SMOOTH EXHAUSTION FUNCTIONS IN CONVEX DOMAINS
\begin{lemma}
    Let $K \subseteq \bbR^{n}$ be a compact set star-shaped with respect to the origin 
    that contains the ball $B_{r}(0)$ and that is contained in the ball $B_{R}(0)$. Then the function 
    \begin{align*}
        f : S \rightarrow \partial K, \quad x \mapsto \arg( \partial K \cap \bbR x )
    \end{align*}
    satisfies 
    \begin{align*}
        R^{2}/r % euclidean 
    \end{align*}
    If $K$ is convex, then 
    \begin{align*}
        g : S \rightarrow \bbR, \quad x \mapsto \| \bbR x \cap \partial K \|
    \end{align*}
    satisfies 
    \begin{align*}
        R \sqrt{ R^{2} / r^{2} - 1 } % angular distance 
        \\
        \frac R r \sqrt{ R^{2} - r^{2} } % angular distance 
    \end{align*}
\end{lemma}
\begin{proof}
    .
\end{proof}

>>>>

The situation is less clear cut when we study the curl or divergence operators in vector calculus.
We use the vector field spaces
\begin{align*}
    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
    ,
    \\
    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
    .
\end{align*}
Their members are vector fields whose distributional curls and divergences are in Lebesgue spaces. 
This only requires that certain sums of distributional partial derivatives are integrable, 
and hence these spaces are not classical Sobolev spaces of vector fields. 
Our objective is to find bounded potentials for the operators 
\begin{align*}
    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
    \qquad 
    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
\end{align*}
The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
We are interested in constants for inequalities such as 
\begin{align*}
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
    \| \bfv \|_{L^{p}(\Omega)}
    \leq 
    C_{\curl,\Omega,p}
    \| \bff \|_{L^{p}(\Omega)}
    ,
    \qquad 
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
    \| \bfv \|_{L^{p}(\Omega)}
    \leq 
    C_{\divergence,\Omega,p}
    \| f \|_{L^{p}(\Omega)}
    ,
\end{align*}
and whether these constants can be estimated by the operator norms of linear potential operators 
\begin{align*}
    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
    ,
    \\
    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
    .
\end{align*}

@@

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
        M := |\patch_{\calT}(S)| \setminus T.
    There exists a bi-Lipschitz mapping
        \varphi : T \rightarrow M
    satisfying
        \Lip( \varphi,      T ) \leq \Cvier{n}{k} \diam(T),
        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k} \diam(T),
    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$
\end{theorem}
\begin{proof}
    We derive the estimate in several steps. 
    \begin{itemize}

@@

        We begin with the following preparatory observations. 

@@

        We let $A_{T} \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.

@@

            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x

@@

            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x

@@

            \left( \vecone \cdot A_{T}^{-1} x \right)

@@

            \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} x \right)

@@

            2 \left| \vecone \cdot A_{T}^{-1} x \right|

@@

            2 \sqrt{n} \cdot \sigma_{\max}(A_{T}^{-1}) 

@@

        \todo{Find the best estimate. }

@@

                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y

@@

                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y

@@

                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y

@@

            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 

@@

            \left| \|A_{T}^{-1} x\|_2 - \|A_{T}^{-1} y\|_2 \right|

@@

            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{T}^{-1}) 

@@

        where $\| A_{T}^{-1} y \|_{1} \leq \| A_{T}^{-1} x \|_{1}$ without loss of generality, we find 

@@

                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y

@@

                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y

@@

                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y

@@

            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } 

@@

            \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} }

@@

            2 \sigma_{\min}(A_{T}^{-1})^{-1} 

@@

        We recall that $\sigma_{\max}(A_{T}^{-1}) = \sigma_{\min}(A_{T})^{-1}$ and $\sigma_{\min}(A_{T}^{-1})^{-1} = \sigma_{\max}(A_{T})$.

        \item 
        Without loss of generality, the barycenter of $S$ is the origin. 
        Let $I := M \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        So $J$ is in the boundary of $|\calT|$ and is disjoint from $S$.
        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
        Note that $J$ is the union of exactly those faces of $T$ that contain $S'$.

        \item 
        We construct a new triangulation that contains $T$ and that is a star around $S$.
        For that purpose, we let $z'_{S}$ be the midpoint of $S'$. 
        We first define a new triangulation $\calS$ by the barycentric refinement of $T$. 
        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.

        We define another simplicial complex $\calS^c$ as follows:
        whenever $K \in \calS$ is an $n$-simplex, 
        we replace the vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
        giving us a simplex $K'$.

        \item 
        In what follows, we also use $\calR'$, 
        the simplicial complex obtained from $\calS'$ by barycentric subdivision of $S$.
        Then $\calR'$ is the local star around the barycenter $z_S$,
        and all $n$-simplices in $\calR'$ contain $z_{S}$. 
        We let $\calR$ and $\calR^{c}$ be the corresponding refinements of $\calS$ and $\calS^{c}$, respectively.

        \item 
        % \todo{Reflect onto complement and estimate bi-Lipschitz constant}
        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$.
        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
        be affine reference transformations
        that agree on the vertices common to $K$ and $K'$.
        We then define 
        \begin{align*}
            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
        \end{align*}
        Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
        \begin{align*}
            \| \Jacobian \Theta_{|K}      \| \leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
            \qquad 
            \| \Jacobian \Theta_{|K}^{-1} \| \leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
        \end{align*}

        \item 
        % \todo{Combine all this to get the final transformation.}
        We let $\calK$ the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$. 
        Using our initial observations, we obtain homeomorphisms 
        \begin{align*}
            \Psi_{\calK } : |\calK| \rightarrow \calB,
            \qquad 
            \Psi_{\calR'} : |\calR'| \rightarrow \calB.
        \end{align*}
        Both $\Psi_{\calK}$ and $\Psi_{\calR'}$ map $T$ onto the same subset of the unit ball.
        Consequently, the image under $\Psi_{\calK}$ of $\overline{|\calK| \setminus T}$
        onto the image under $\Psi_{\calR'}$ of $|\calR^{c}|$.
        It follows that 
        \begin{align*}
            \Theta_{S} := \Psi_{\calK}^{-1} \Psi_{\calR'} \Theta
        \end{align*}
        is a mapping from $T$ onto $\overline{\patch_{\calT}(S) \setminus T}$.
        We estimate the Jacobians: 
        \begin{align*}
            \| \Jacobian \Theta_{S} \| 
            \leq 
            \sup_{ K \in \calK  }
            2 \sigma_{\min}(A_{K}^{-1})^{-1} 
            \sup_{ K \in \calR' } 
            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{K}^{-1}) 
            \sup_{ K \in \calR  } \kappa(A_{K})
            .
        \end{align*}
        Each bisection halves the volume of the triangles. Thus,
        \begin{align*}
            \color{red}
            \| \Jacobian \Theta_{S} \| 
            &\leq 
            2 \sup_{ K \in \patch_{\calT}(S) }
            2 \sigma_{\min}(A_{K}^{-1})^{-1} 
            4 \sup_{ K \in \patch_{\calT}(S) } 
            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{K}^{-1}) 
            4 \sup_{ K \in \patch_{\calT}(S) } 
            \kappa(A_{K})
            \\&\leq 
            64
            \left( \sqrt{n} + 1 \right) 
            \sup_{ K \in \patch_{\calT}(S) }
            \sigma_{\max}(A_{K}     ) 
            \sup_{ K \in \patch_{\calT}(S) } 
            \sigma_{\max}(A_{K}^{-1}) 
            \sup_{ K \in \patch_{\calT}(S) } 
            \kappa(A_{K})
            .
        \end{align*}
        That establishes the final estimate.

%         \item 
%         Suppose that $S = \{v_0\}$ is a single vertex. 
%         We construct a transformation from the vertex star around $S$ onto the Euclidean unit ball. 
%         Without loss of generality, $S$ is at the origin. 
%         For any $T \in \patch_{\calT}(S)$, we let $F_T$ be the transformation. 
%         We define $F$ over $|\patch_{\calT}(S)|$ piecewise. 
%         \todo{Complete}
%

%         \item 
%         Let $\calU$ be the simplicial complex of dimension $n-1$ that contains precisely those facets of $T$ that do not contain $S$.
%         We write $Y := F( |\calU| )$. 
%         \todo{Shape of the outer patch $Y$, star-shaped geometry}
%         
%         \item 
%         We let $\sphere{n}_{\star} := \sphere{n} \setminus \{e_{n+1}\} \subseteq \bbR^{n+1}$ be the unit sphere without the North pole. 
%         Suppose that $\bar x \in \sphere{n}$ is a point on the unit sphere and $\bar x \neq e_{n+1}$. 
%         We define its stereographic projection as 
%         \begin{align}
%             \pi( \bar x ) 
%             = 
%             \sum_{i=1}^{n} \frac{x_i}{1 - x_{n+1}} e_{i}
%             .
%         \end{align}
%         This is a mapping $\pi : \sphere{n}_{\star} \rightarrow \bbR^{n}$. 
%         Its inverse is defined as follows: given $y \in \bbR^{n}$, we have 
%         \begin{align}
%             \pi^{-1}( y )
%             = 
%             \sum_{i=1}^{n} \frac{2 y_i}{1 + \| y \|^2} e_{i}
%             +
%             \frac{1 - \| y \|^2}{1 + \| y \|^2} e_{n+1}
%             .
%         \end{align}
%         \item 
%         Mirroring the unit sphere along the equator is expressed in stereographic coordinates by the involution 
%         \begin{align}
%             \mu : \bbR^{n} \rightarrow \bbR^{n},
%             \qquad 
%             y \mapsto \frac{y}{\| y \|}.
%         \end{align}
%         \item 
%         \begin{align}
%             G(y) := \| y \| \cdot \phi\left( \frac{y}{\|y\|} \right)^{-1} \frac{y}{\|y\|}
%         \end{align}
%         \item 
%         We combine these mappings:
%         \begin{align}
%             Q : \sphere{n} \rightarrow \sphere{n}, \qquad x \mapsto \pi^{-1} G^{-1} \mu G \pi(x)
%         \end{align}
%         We want to analyze its Lipschitz properties. \todo{Stuff}
%         \item
%         We have constructed a bi-Lipschitz mapping from the Euclidean unit sphere into itself.
%         We use the following result~\cite[Theorem~3]{alestalo2018radial}:
%         if $f : \sphere{n} \rightarrow \sphere{n}$ is any $L$-Lipschitz mapping from the Euclidean unit sphere into itself, 
%         then the radial extension $f : \ball{n} \rightarrow \ball{n}$ is an $L$-Lipschitz mapping from the Euclidean unit ball into itself.
%         Consequently, \todo{write out}
%         \item 
%         In total, we thus have 
%         \begin{align}
%             Q' := F^{-1} \pi^{-1} G^{-1} \mu G \pi F
%             .
%         \end{align}
    \end{itemize}
\end{proof}
